Data_Import

### 2023-04-20 Data_Import.Rmd
Finalized code for final presentation.

#Lets make some new variables 
      #Duration of treatment
                     Duration = as.factor(
                       ifelse(Days_complete_1>0 & Days_complete_1 <=5, "1-5",
                       ifelse(Days_complete_1>5 & Days_complete_1 <=10, "6-10",
                       ifelse(Days_complete_1>10 & Days_complete_1 <=15, "11-15", "16+"
                              )))))

@@

ggplot(data = subset(Mothership, !is.na(TxYear)),mapping = aes(x = TxYear))+
  geom_bar(color = "black",fill="#9350C7")+
  ggtitle("Frequency of Patients per Year") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Year")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

>>>>

#Lets make some new variables 
      #Duration of treatment
                     Duration = as.factor(
                       ifelse(Days_complete_1>0 & Days_complete_1 <=5, "1",
                       ifelse(Days_complete_1>5 & Days_complete_1 <=10, "2",
                       ifelse(Days_complete_1>10 & Days_complete_1 <=15, "3", "4"
                              )))),
                    Duration = recode(Duration,
                                      "1"="1-5",
                                      "2"="6-10",
                                      "3"="11-15",
                                      "4"="16+"
                                      ))

@@

ggplot(data = subset(Mothership, !is.na(TxYear)),mapping = aes(x = TxYear))+
  geom_bar(color = "black",fill="#9350C7")+
  ggtitle("Frequency of Patients per Year") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Year")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,1500))
